---
title: "Creating Cross-Stitch Patterns of Images Using K-Means Clustering"
subtitle: "STA314H1 - Fall 2020"
author: "Ziyue Yang"
date: "November 3^rd^, 2020"
output: pdf_document
---

```{r knitsetup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

# Introduction

This article demonstrates how to make a cross-stitch pattern of images, based on 
the k-means clustering algorithm.

## Setup

It is required for you to use the following libraries. Note that if you don't have any of these, undo the commenting before you run:

```{r libraries, message=FALSE}
# Uncomment the following if need to install libraries
# install.packages("imager")
# install.packages("tidyverse")
# install.packages("tidymodels")
# install.packages("sp")
# install.packages("scales")
# install.packages("cowplot") 
# devtools::install_github("sharlagelfand/dmc")

library(imager)
library(tidyverse)
library(tidymodels)
library(sp)
library(scales)
library(cowplot)
library(dmc)
```

In addition, we load the script `functions.R`, which will provide us the functions we are going to demonstrate:

```{r loadfunctions}
source('functions.R')
```

The script `functions.R` contains the following functions:

a. `process_image()`

b. `scree_plot()`

c. `colour_strips()`

d. `make_pattern()`

For demonstration, let's make a cross-stitch pattern of a Warhol screenprint of Elizabeth Taylor:

```{r}
plot(imager::load.image('sakura.jpg'))
```

## Workflow

Our work flow can be briefly described as:

$$\text{Get Cluster Data for Multiple }K's \rightarrow \text{Choose Ideal }K\rightarrow \text{Make Cross-Stitch Pattern with Chosen $K$.} $$

# Generating Cross-Stitch Patterns

Before we begin, let's go over the functions we need to make a cross-stitch pattern.

## `process_image()`

Function `process_image()` allows us to retrieve the cluster information based on a list of k's.

This function takes two inputs:

- `image_file_name`: the path of the image you want to cluster;

- `k_list`: a list of numbers of centers in the clustering. For instance, if we want to cluster the image with 2, 3, 7 
cluster centers respectively, then `k_list` takes `c(2, 3, 7)` as the input.

Calling the function as shown below allows us to retrieve the clustering information
of the Warhol picture, from 1 to 10 cluster centers. We want to choose the best number of cluster centers later:

```{r}
cluster_info <- process_image('sakura.jpg', c(5:6))
```

The output of `process_image()` stores information in variable `cluster_info`, for every k in `k_list`. 

For each k, the output contains

- `kclust`: the output of calling `kmeans(x = select(image_dat, c(-x, -y)), centers = .x, nstart = 5)`;

- `tidied`: the tidied data of `kclust`, i.e. `tidy(kclust)`;

- `glanced`: the `glance` of `kclust`.

Let's check the output of each of the above, for `k = 2`:

```{r}
cluster_info$kclust[[2]]
cluster_info$tidied[[2]]
cluster_info$glanced[[2]]
```

**Note**: From now on, `cluster_info` will store all the clustering information
of the Warhol image, which will be used as the input for the following functions.

## `scree_plot`

This function takes the input `cluster_info`, as produces a scree plot based on 
`glanced`:

and returns a scree plot, with respect to the maximum numbers of cluster centers in `k_list` we inputted for `process_image()` (10 in this case):

```{r}
scree_plot(cluster_info)
```

Note that it's hard to tell what number of centers to choose based on scree plot. Let's try the ratio version:

```{r}
clusterings <- cluster_info %>% unnest(cols = c(glanced))
nclust = length(clusterings$k) 
ratio = rep(NA, nclust-1)
for (kk in 2:nclust) {
  ratio[kk-1] = clusterings$tot.withinss[kk]/clusterings$tot.withinss[kk-1] 
}
plot_data <- data.frame(k = clusterings$k[2:nclust],ratio)
ggplot(plot_data, aes(x = k, y = ratio)) + geom_line()
```

From which we can tell that the number of clusters seems to be 5.

## `colour_strips()`

This function takes the input `cluster_info`, and produces the DMC colour strips that are closest to the RGB colours of cluster centers,  for each k in `k_list`.

```{r}
colour_strips(cluster_info)
```

Looks like 5 is a good option. Let's use 5 centers to make our cross-stitch pattern!

## `make_pattern()`

Finally, this function allows us to plot the cross-stitch of our image. This function
takes several inputs:

- `cluster_info`: The output of `process_image`.

- `k`: The number of cluster centers.

- `x_size`: The total number of possible stitches in the horizontal direction.

- `black_white`: The logical value indicating whether the cross-sitch will be plotted in 
black and white. Default is `FALSE`, such that we have a cross-stitch where the i^th cluster has 
the DMC colour that is closest to the RGB colour of the i^th^ cluster center.

- `background_colour`: The colour of the background. Default is `NULL`, such that we have 
a transparent background.

Here is where things are getting exciting. Let's make a $60\times 60$ colourful cross-stitch of Elizabeth Taylor's picture, with 4 cluster centers:

```{r}
make_pattern(cluster_info, 6, 100)
```

or, if we prefer a black-and-white version:

```{r}
make_pattern(cluster_info, 5, 60, black_white = TRUE)
```

Furthermore, we can make a colourful one with light green blackground:

```{r}
make_pattern(cluster_info, 5, 60, background_colour = "light green")
```

# Session Information

```{r, echo = FALSE}
sessionInfo()
```
